### 2019-12-25 Sections/cryptowars.tex
QDS nearly done - needs references & minor more precise description of channel errors

The security of such a scheme comes from the fact that $f$ is difficult to invert, and therefore an adversary who has access to only the public key cannot find the secret key in order to provide a valid (forged) signature.

@@

In 2001, Gottesman and Chuang \cite{} proposed the first QDS protocol. The idea is to use
the non-orthogonality of state to realize a ``quantum one-way function".

>>>>

The security of such a scheme comes from the fact that $f(x)$ is classically difficult to invert, and therefore an adversary who has access to only the public key cannot find the secret key in order to provide a valid (forged) signature. However, any scheme that is based on computational-complexity arguements cannot offer information-theoretic security, and schemes based purely on the physics of quantum mechanics are much more desirable.

@@

In 2001, Gottesman and Chuang \cite{} proposed the first QDS protocol. The idea is to use
the non-orthogonality of state to realize a ``quantum one-way function", where the difficulty to invert the function is based on the laws of physics rather than computational complexity.

Here if we have a quantum state $\ket{f(x)}$ based on the classical description $f(x)$, no one should be able to determine $f(x)$ with high probability, unless they are the authentic party. The function $f$ does not need to be classically difficult, since the one-wayness in the classical protocol is replaced by non-orthogonality in the quantum analogue.
	% 
	\begin{enumerate}
\item A function $f$ is chosen and is made public, it takes the input $x$ and generates $f(x)$ that describes the quantum state.
 % 
\item Key generation: for the private key, Alice chooses a pair of bit-string 
$\{x_0^i,x_1^i\}$ where $1\leq i \leq L$. The bit-string $x_0$ ($x_1$) will be used to sign the 0's (1's) in the message. $L$ is determined by the security level required.
% 
\item For the public key, Alice generates multiple copies of $\{\ket{x_0^i},\ket{x_1^i}\}$. She distributes to each receiver the corresponding states. To check that the public keys are the same, each of the receivers interact by performing SWAP tests. This provides an affirmative answer without disturbing the states, if two are identical.
% 
\item Signing: to sign a message, Alice chooses the mesasge vale $b$, and sends $(b,x_b^i)$ to the receiver. This can be done classically
\item Verification: the receiver uses $x_b^i$ and generates the corresponding quantum state
$\ket{f(x)_b^i}$ and checks whether this is consistant with the stored public key.
\end{enumerate}

Whilst the GC-QDS protocol is intuitive, it is also highly impractical due to the experimental requirements. Firstly, the protocol requires for long-storage quantum memories, since the signature and the verification can be separated by long periods of time -- this requirement is one of the major bottle-necks for building a scalable quantum computer. Secondly, multiple copies of the public key is needed, and each reciving party need to perform the SWAP test, the latter involves more quantum communication and ancillary qubits

\subsubsection{A practical QDS protocol}

Since the development of the GC-QDS protocol, the field has undergone major developments and lifted all the restricting requirements of the protocol.

Quantum memory - the storage of the quantum state until verification renders the scheme impractical. The idea is to replace the quantum public key with a classical verification key, which is now different for all the receivers \cite{}.

After removing the quantum memory requirement, the other experimentally challenging task is ensuring that the same quantum public key was send to different receivers. This step can be bypassed by adding an extra step, replacing the state comparison SWAP test with a "symmetrization". This step ensures that even if the states distributed by Alice are not identical, the classical verification keys shared by the receivers will be symmetric.

% We explain the the symmetrization protocol here: Alice selectsx

Making the public keys (or verification keys) different for each receiver.

Now we are able to describe a memory-less QDS protocol that can be realized with the same technology as QKD. The protocol works for three parties, but can be generalised.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QDS():
\begin{enumerate}
% 
	\item Key generation: Alice performs the first part of a QKD protocol separately, twice with
	Bob and Charlie. Alice has has four bit strings $A_0^B, A_1^B, A_0^C, A_1^C$, Bob has two strings $K_0^B, K_1^B$, and Charlie has $K_0^C, K_1^C$. The private key $sk$ is the concatenation of the two corresponding strings, $sk=(A_0^B||A_0^C, A_1^B||A_1^C)$. At this stage, error rates of the quantum channel are estimated.
	% 
	\item Bob and Charlie perform a symmetrization by exchanging secretly half of their strings (via another QKD link). The new strings for Bob are $S_0^B, S_1^B$ and Charlie $S_0^C,S_1^C$. They are composed from half of the string initially sent to Bob and half of that to Charlie,, but which part from Bob and Charlie's initial strings is unknown to Alice.
	% 
	\item The verification keys for Bob and Charlie are $pk_B = (S_0^B,S_1^B)$, and 
	      $pk_C=(S_0^C,S_1^C)$.
	% 
	\item Signing: to sign a message $M$, Alice sends $(M, A_M^B||A_M^C)$ to Bob.
	% 
	\item Verification: Bob checks the mismatch rate between the signature received 
	      $A_M^B||A_M^C$ and his stored verification key $S_M^B$. If the error is compatible with the channel noise, he accepts. Charlie receives a message with Alice's signature, but from Bob. He performs a similar check and may choose to accept the message as having originated from Alice. 
\item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{A quantum digital signature (QDS) protocol compatible with a QKD network.}\label{alg:qds}
\end{table}
